### 2023-01-27 Poisot_2023_guidelines_prediction_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@03944f45cb3ceab9378f415b05e746b5f347c090 🚀

\begin{enumerate}
    \itemThe prediction of species interactions is gaining momentum as a
way to circumvent limitations in data volume. Yet, ecological networks
are challenging to predict because they are typically small and sparse.
Dealing with extreme class imbalance is a challenge for most binary
classifiers, and there are currently no guidelines as to how predictive
models can be trained for this specific problem.%
    \itemUsing simple mathematical arguments and numerical experiments
in which a variety of classifiers (for supervised learning) are trained
on simulated networks, we develop a series of guidelines related to the
choice of measures to use for model selection, and the ways to assemble
the training dataset.%
    \itemNeither classifier accuracy nor the area under the receiver
operating characteristic curve (ROC-AUC) are informative measures for
the performance of interaction prediction. The area under the
precision-recall curve (PR-AUC) is a fairer assessment of performance.
In some cases, even standard measures can lead to selecting a more
biased classifier because the effect of connectance is strong. The
amount of correction to apply to the training dataset depends on network
connectance, on the measure to be optimized, and only weakly on the
classifier.%
    \itemThese results reveal that training machines to predict networks
is a challenging task, and that in virtually all cases, the composition
of the training set needs to be fine-tuned before performing the actual
training. We discuss these consequences in the context of the low volume
of data.%
\end{enumerate}

>>>>

\begin{enumerate}
    \item The prediction of species interactions is gaining momentum as
a way to circumvent limitations in data volume. Yet, ecological networks
are challenging to predict because they are typically small and sparse.
Dealing with extreme class imbalance is a challenge for most binary
classifiers, and there are currently no guidelines as to how predictive
models can be trained for this specific problem.%
    \item Using simple mathematical arguments and numerical experiments
in which a variety of classifiers (for supervised learning) are trained
on simulated networks, we develop a series of guidelines related to the
choice of measures to use for model selection, and the ways to assemble
the training dataset.%
    \item Neither classifier accuracy nor the area under the receiver
operating characteristic curve (ROC-AUC) are informative measures for
the performance of interaction prediction. The area under the
precision-recall curve (PR-AUC) is a fairer assessment of performance.
In some cases, even standard measures can lead to selecting a more
biased classifier because the effect of connectance is strong. The
amount of correction to apply to the training dataset depends on network
connectance, on the measure to be optimized, and only weakly on the
classifier.%
    \item These results reveal that training machines to predict
networks is a challenging task, and that in virtually all cases, the
composition of the training set needs to be fine-tuned before performing
the actual training. We discuss these consequences in the context of the
low volume of data.%
\end{enumerate}
